TORs2 and 3

### 2024-02-05 Ecov_study/recruitment_functions/presentation/SRR_presentation.Rmd
presentation formatting
cleaning up slide levels and theme

---
title: "TORs2 and 3"
output: beamer_presentation
fig_caption: FALSE
slide_level: 3
theme: "Darmstadt"
titlegraphic: WHOI_NOAA_logo_smaller.png
date: "`r Sys.Date()`"
---

@@

@@

* need to make the logo smaller on title and content slides (put it in the footer)

@@

@@

@@

@@

@@

## Analysis

\begin{enumerate}
  \item Convergence of the estimating models
  \item Model identifiability of an underlying stock recruitment model and/or an underlying relationship
   between environmental covariate 
  \item $\delta$AIC and model probability
  \item Assessment error (recruitment, spawning stock biomass, and Fbar)
  \item Bias of estimated parameters
  \item Mohn's $\rho$
  \item Projection performance relative to assumptions about the environmental covariate
\end{enumerate}

@@

## Slide with Plot

```{r pressure}
plot(pressure)
```

>>>>

---
title: "TORs2 and 3"
output: beamer_presentation
fig_caption: FALSE
theme: "Singapore"
slide-level: 3
# titlegraphic: WHOI_NOAA_logo_smaller.png
header-includes: 
- \addtobeamertemplate{title page}{\centering \includegraphics[width=16.5cm]{WHOI_NOAA_logo_smaller.png}\par }{}
classoption: "aspectratio=169"
date: "`r Sys.Date()`"
---

@@

# TORs

## TOR 2

- paste TOR2

## TOR3

- paste TOR3

@@

<!-- * need to make the logo smaller on title and content slides (put it in the footer) -->

@@

# Background

@@

# Inputs

@@

# OM

@@

# EM

@@

# Analysis & Results

## Analyses

\begin{enumerate}
  \item Convergence of the estimating models
  \item Model identifiability of an underlying stock recruitment model and/or an underlying relationship
   between environmental covariate
  \item $\Delta$AIC and model probability
  \item Assessment error (recruitment, spawning stock biomass, and Fbar)
  \item Bias of estimated parameters
  \item Mohn's $\rho$
  \item Projection performance relative to assumptions about the environmental covariate
\end{enumerate}

## Convergence

## Model Identifiability

##  $\Delta$AIC and model probability

## Assessment error (recruitment, spawning stock biomass, and Fbar)

## Bias of estimated parameters

## Mohn's $\rho$

## Projection performance relative to assumptions about the environmental covariate

# Conclusions

## Take-aways
- These are the take-aways (copy from WP)

# Future Work

## List of what's next

- This is what we suggest for follow-up

---

Acknowledgements

- This work could not have been completed without the use of Azure computing (NOAA) and MIT (... greg to fill in)
- We thank other members of the SSRTWG for thoughtful comments during earlier discussions and presentations of this work

@@

<!-- ## Slide with Plot -->

<!-- ```{r pressure} -->
<!-- plot(pressure) -->
<!-- ``` -->
